Influence of Connectivity on Dung Beetle Communities

### 2025-05-21 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
answered some questions

2) Is there anything about these species that might be interesting in the context of corridors?
  - are any species known to be good fliers/movers?
  - specialists on deer dung?
  - navigate by starlight?
  - feeding preferences?

>>>>

cvig - open sand chaparral, open grassland preference nealis 1977
mbis - open sand chapparal preference nealis 1977
open - slight preference towards open chap and shaded chap, little open grassland nealis 1977

pign - sharing forest habitat but need more info conover 2019
pvin - open habitat but share forest with pign conover 2019
alec - forest preference conover 2019

2) Is there anything about these species that might be interesting in the context of corridors?
  - are any species known to be good fliers/movers?
    - Ospina 2018 -> wing shape py habitat preference and differences in wing shape determined by species groupings
    ^ beetles with wider wings showed more preference towards open habitat, contrary to what is already known in literature on other taxa (butterflies)
    ^ large body beetles tending towards lower energy flight strategies. maybe justification for corridor preference?

    = stanbrook and king 2022 -> tunnelers prefering open habitat and tunnelers also contributing more towards dung removal.

  - specialists on deer dung?
    - Conover 2019 -> dung source being less of an issue than habitat type but some species were more responsive to specific bait types so future studies should use a mix of multiple bait types

  - navigate by starlight?
  - feeding preferences?
